Pool Model

### 2025-08-21 pool_model.tex
Add labels to the equations

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

    \label{eq:ODE_tempshift}

@@

@@

        (a) The time dependence of the total bacterial count $N$ for the model including the back-flow to the lag phase due to temperature stress~(\ref{eq:ODE_tempshift}).

@@

@@

@@

@@

\label{Mut_Inhib}

@@

@@

@@

   \label{eq:model_ODE}

@@

@@

@@

This system of equations defines the microenvironment $\mbm$ and bacteria state matrix $\mbx$ as
\begin{equation}
    \mbm = R, \hspace{1cm}
    \mbx = \begin{pmatrix}
        L_A & L_B \\
        G_A & G_B 
    \end{pmatrix}.
\end{equation}
%

>>>>

\label{eq:reactions_3pools}

@@

\label{eq:reactions_resource}

@@

\label{eq:resource}

@@

\label{eq:lagtime_deriv1}

@@

\label{eq:lagtime_deriv2}

@@

\label{eq:lagtime_deriv3}

@@

\label{eq:lagtime}

@@

\label{eq:reactions_backlag}

@@

\label{eq:rate_backlag}

@@

\label{eq:rate_backlag2}

@@

\label{eq:rate_backlag3}

@@

@@

\label{eq:ode_tempshift_backlag}

@@

        (a) The time dependence of the total bacterial count $N$ for the model including the back-flow to the lag phase due to temperature stress~(\ref{eq:ode_tempshift_backlag}).

@@

\label{eq:ode_inhib1}

@@

\label{eq:ode_inhib_B}

@@

\label{eq:ode_inhib2}

@@

@@

\label{eq:ode_inhib3}

@@

\label{eq:ode_inhib_psi}

@@

\label{eq:model_ODE_x}

@@

\label{eq:N_pro_species}

@@

\label{eq:N_total}

@@

This system of equations defines the microenvironment $\mbm$ and bacteria state matrix $\mbx$ as
\begin{equation}
    \mbm = R, \hspace{1cm}
    \mbx = \begin{pmatrix}
        L_A & L_B \\
        G_A & G_B 
    \end{pmatrix}.
\label{eq:gLV_x_m}
\end{equation}
%
